% !TeX root = ../../thesis.tex
\chapter{Scientific Contributions}\label{ch:publications}

\section*{Journal Articles}

\textbf{Papadopoulou, A.}, Pintor-Monroy, M. I., Dayaran, S., Skvortsova, I., Dos Anjos, J.P., Subramaniam, S., Song, W., Lieberman, I., Kuang, Y., Hofkens, J., Roeffaers, M. B. J., Bals, S., Gehlhaar, R., \& Genoe, J. (2025). Electron Transport Layer Optimization for All-Inorganic, Vacuum-Deposited Perovskite-Based Photodiodes with Improved Reverse Bias Stability and High Speed. Under Review

\textbf{Papadopoulou, A.}, Saha, R. A., Pintor-Monroy, M. I., Song, W., Lieberman, I., Solano, E., Roeffaers, M. B. J., Gehlhaar, R., \& Genoe, J. (2024). In situ annealing effect on thermally co-evaporated CsPbI2Br thin films studied via spectroscopic ellipsometry. ACS Applied Materials \& Interfaces, 16(36), 47889–47901. https://doi.org/10.1021/acsami.4c09283

Saha, R. A., \textbf{Papadopoulou, A.}, Ariza García, R., Degutis, G., Skvortsova, I., Braeckevelt, T., De Angelis, F., Solano, E., Dos Anjos, J. P. de S. G., Pintor Monroy, M. I., Mongilyov, I., Goderis, B., Rubio-Zuazo, J., Genoe, J., Meneghini, C., Steele, J. A., Bals, S., Van Speybroeck, V., Hofkens, J., \& Roeffaers, M. B. J. (2025). Generating a Stable Higher-Symmetric CsPbI3 Black Phase in Ambient Conditions: Unveiling the Stabilization Mechanism. Under Review

Siddik, A. B., Georgitzikis, E., Song, W., \textbf{Papadopoulou, A.}, Zaman, A. U., Lim, M. J., Pejovic, V., Lieberman, I., Malinowski, P. E., Genoe, J., Conard, T., Cheyns, D., \& Heremans, P. (2024). PbS and InAs quantum-dot thin films for short-wave infrared detectors. ACS Applied Nano Materials, 7(22), 25412–25422. https://doi.org/10.1021/acsanm.4c04386

Annavarapu, N., Goldberg, I., \textbf{Papadopoulou, A.}, Elkhouly, K., Genoe, J., Gehlhaar, R., \& Heremans, P. (2023). Scattered emission profile technique for accurate and fast assessment of optical gain in thin film lasing materials. ACS Photonics, 10(5), 1583–1590. https://doi.org/10.1021/acsphotonics.3c00204


\section*{Conference Contributions}

\textbf{Papadopoulou, A.}, Saha, R. A., Pintor-Monroy, M. I., Song, W., Lieberman, I., Solano, E., Roeffaers, M. B. J., Gehlhaar, R., \& Genoe, J. (2024). Dynamic Model Development for the Temperature-Dependent Characterization of CsPbI2Br Perovskite Thin Films via Spectroscopic Ellipsometry. MRS Fall Meeting 2024 (Oral Presentation)

\textbf{Papadopoulou, A.}, Saha, R. A., Pintor-Monroy, M. I., Song, W., Lieberman, I., Solano, E., Roeffaers, M. B. J., Gehlhaar, R., \& Genoe, J. (2025). Speed and Reliability Enhancement for Vacuum-Deposited \ch{CsPbI_2Br} Photodiodes in the Reverse Bias Regime Through Tailored Engineering of the Electron Transport Layer. nanoGe International Conference on Perovskite Thin Film Photovoltaics and Perovskite Photonics and Optoelectronics (NIPHO25) (Oral Presentation)

Kang, S., Benelajla, M., Ciamain, R. M., Ali, F., \textbf{Papadopoulou, A.}, Shramkova, O., Witters, L., De Vos, J., Malinowski, P. E., Heremans, P., Le Thomas, N., Figeys, B., Gehlhaar, R., \& Genoe, J. (2023). Wafer-level-integrated vertical-waveguide sub-diffraction-limited color splitters. 2023 International Electron Devices Meeting (IEDM), 1–4.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Keep the following \cleardoublepage at the end of this file, 
% otherwise \includeonly includes empty pages.
\cleardoublepage

% vim: tw=70 nocindent expandtab foldmethod=marker foldmarker={{{}{,}{}}}
